---
title: "Framingham"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dygraphs)
ProjTemplate::reload()
load('data/rda/TimeAndFractures.rda') # Data with fracture time, and death time
load('data/rda/predictors.rda') # Data with predictors
dat_annual_orig <- dat_attend_orig %>% filter(!is.na(YrFrac)) %>%
  nest(-PID) %>%
  mutate(yrs_5yr_risk = map(data, ~seq(.$YrFrac-4, .$YrFrac))) %>%
  select(-data) %>%
  unnest() %>%
  mutate(risk_5yr = 1) %>%
  right_join(dat_orig,
             by = c('PID' = 'PID', 'yrs_5yr_risk' = 'yrs')) %>%
  mutate(risk_5yr = ifelse(is.na(risk_5yr), 0, 1)) %>%
  rename(yrs = yrs_5yr_risk)

bl <- dat_attend_orig %>% filter(!is.na(YrFrac)) %>% 
  nest(-PID) %>% 
  mutate(yrs_10yr_risk = map(data, ~seq(.$YrFrac-9, .$YrFrac))) %>% 
  select(-data) %>% 
  unnest() %>% 
  mutate(risk_10yr = 1) %>% 
  right_join(dat_orig, 
              by = c('PID' = 'PID', 'yrs_10yr_risk' = 'yrs')) %>%
  mutate(risk_10yr = ifelse(is.na(risk_10yr), 0, 1)) %>%
  rename(yrs = yrs_10yr_risk)



dat_annual_off <- dat_attend_offspring %>% filter(!is.na(YrFrac)) %>% 
  nest(-PID) %>% 
  mutate(yrs_5yr_risk = map(data, ~seq(.$YrFrac-4, .$YrFrac))) %>% 
  select(-data) %>% 
  unnest() %>% 
  mutate(risk_5yr=1) %>% 
  right_join(dat_offspring, 
             by = c('PID'='PID', 'yrs_5yr_risk' = 'yrs')) %>% 
  mutate(risk_5yr = ifelse(is.na(risk_5yr), 0, 1)) %>% 
  rename(yrs = yrs_5yr_risk)

bl2 <- dat_attend_offspring %>% filter(!is.na(YrFrac)) %>% 
  nest(-PID) %>% 
  mutate(yrs_10yr_risk = map(data, ~seq(.$YrFrac-9, .$YrFrac))) %>% 
  select(-data) %>% 
  unnest() %>% 
  mutate(risk_10yr = 1) %>% 
  right_join(dat_offspring, 
              by = c('PID' = 'PID', 'yrs_10yr_risk' = 'yrs')) %>%
  mutate(risk_10yr = ifelse(is.na(risk_10yr), 0, 1)) %>%
  rename(yrs = yrs_10yr_risk)

transform_orig <- function(d, yr1, yr2){
  tmp <- d %>% filter(age_cur >= yr1 ) 
  if(!is.na(yr2)) tmp <- tmp %>% filter(age_cur < yr2)
  tmp <- tmp %>% 
    group_by(yrs) %>% 
  summarize(N = n(),
            risk_5yr = mean(risk_5yr, na.rm=T)*1000,
            overweight = mean(bmi> 25, na.rm = T),
            obese = mean(bmi > 30, na.rm = T),
            diab = ifelse(sum(!is.na(diab)) > 20, mean(diab, na.rm=T),NA),
            smoking = ifelse(sum(!is.na(smoking))>20, mean(smoking, na.rm=T),NA),
            drinking = ifelse(sum(!is.na(rf_etoh)) > 20, mean(rf_etoh, na.rm= T), NA)) %>%
  filter(N > 30) %>%
  select(-N) 
  return(tmp)
}

transform_off <- function(d, yr1, yr2){
  tmp <- d %>% filter(age_cur >= yr1 ) 
  if(!is.na(yr2)) tmp <- tmp %>% filter(age_cur < yr2)
  tmp <- tmp %>% 
    group_by(yrs) %>% 
  summarize(N = n(),
            risk_5yr = mean(risk_5yr, na.rm=T)*1000,
            diab = ifelse(sum(!is.na(diab)) > 20, mean(diab, na.rm=T),NA),
            smoking = ifelse(sum(!is.na(smoking))>20, mean(smoking, na.rm=T),NA),
            drinking = ifelse(sum(!is.na(rf_etoh)) > 20, mean(rf_etoh, na.rm= T), NA)) %>%
  filter(N > 30) %>%
  select(-N) 
  return(tmp)
}

transform_orig_10<- function(d, yr1, yr2){
  tmp <- d %>% filter(age_cur >= yr1 ) 
  if(!is.na(yr2)) tmp <- tmp %>% filter(age_cur < yr2)
  tmp <- tmp %>% 
    group_by(yrs) %>% 
  summarize(N = n(),
            risk_10yr = mean(risk_10yr, na.rm=T)*1000,
            overweight = mean(bmi> 25, na.rm = T),
            obese = mean(bmi > 30, na.rm = T),
            diab = ifelse(sum(!is.na(diab)) > 20, mean(diab, na.rm=T),NA),
            smoking = ifelse(sum(!is.na(smoking))>20, mean(smoking, na.rm=T),NA),
            drinking = ifelse(sum(!is.na(rf_etoh)) > 20, mean(rf_etoh, na.rm= T), NA)) %>%
  filter(N > 30) %>%
  select(-N) 
  return(tmp)
}

transform_off_10 <- function(d, yr1, yr2){
  tmp <- d %>% filter(age_cur >= yr1 ) 
  if(!is.na(yr2)) tmp <- tmp %>% filter(age_cur < yr2)
  tmp <- tmp %>% 
    group_by(yrs) %>% 
  summarize(N = n(),
            risk_10yr = mean(risk_10yr, na.rm=T)*1000,
            diab = ifelse(sum(!is.na(diab)) > 20, mean(diab, na.rm=T),NA),
            smoking = ifelse(sum(!is.na(smoking))>20, mean(smoking, na.rm=T),NA),
            drinking = ifelse(sum(!is.na(rf_etoh)) > 20, mean(rf_etoh, na.rm= T), NA)) %>%
  filter(N > 30) %>%
  select(-N) 
  return(tmp)
}

```

Age 40-49
=============================================================

Row
-------------------------------------------------------------


### 5 year risk of fracture (per 1000) (**Original**)

```{r}
tmp <- transform_orig(dat_annual_orig, 40, 50)
dygraph(tmp %>% select(yrs, risk_5yr), group='frac')
```

### 5 year risk of fracture (per 1000) (**Offspring**)

```{r}
tmp2 <- transform_off(dat_annual_off, 40, 50)
dygraph(tmp2 %>% select(yrs, risk_5yr), group='frac_off')
```

Row
---------------------------------------------------------------------

### Prevalence of obesity (**Original**)

```{r}
dygraph(tmp %>% select(yrs, obese), group = 'frac') %>% 
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of obesity (**Offspring**)

```{r}

```


Row
---------------------------------------------------------------------------

### Prevalence of diabetes (**Original**)

```{r}
dygraph(tmp %>% select(yrs, diab),  group = 'frac') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of diabetes (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, diab),  group = 'frac_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

Row
-----------------------------------------------------------------

### Prevalence of smoking (**Original**)

```{r}
dygraph(tmp %>% select(yrs, smoking), group = 'frac') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of smoking (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, smoking), group = 'frac_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

Row
----------------------------------------------------------------------

### Prevalence of heavy drinking (**Original**)

```{r}
dygraph(tmp %>% select(yrs, drinking), xlab='Year', group='frac') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```


### Prevalence of heavy drinking (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, drinking), xlab='Year', group='frac_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

Age 50-59
=============================================================

Row
-------------------------------------------------------------


### 5 year risk of fracture (per 1000) (**Original**)

```{r}
tmp <- transform_orig(dat_annual_orig, 50, 60)
dygraph(tmp %>% select(yrs, risk_5yr), group='frac2')
```

### 5 year risk of fracture (per 1000) (**Offspring**)

```{r}
tmp2 <- transform_off(dat_annual_off, 50, 60)
dygraph(tmp2 %>% select(yrs, risk_5yr), group='frac2_off')
```

Row
---------------------------------------------------------------------

### Prevalence of obesity (**Original**)

```{r}
dygraph(tmp %>% select(yrs, obese), group = 'frac2') %>% 
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of obesity (**Offspring**)

```{r}

```


Row
---------------------------------------------------------------------------

### Prevalence of diabetes (**Original**)

```{r}
dygraph(tmp %>% select(yrs, diab),  group = 'frac2') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of diabetes (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, diab),  group = 'frac2_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

Row
-----------------------------------------------------------------

### Prevalence of smoking (**Original**)

```{r}
dygraph(tmp %>% select(yrs, smoking), group = 'frac2') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of smoking (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, smoking), group = 'frac2_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

Row
----------------------------------------------------------------------

### Prevalence of heavy drinking (**Original**)

```{r}
dygraph(tmp %>% select(yrs, drinking), xlab='Year', group='frac2') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```


### Prevalence of heavy drinking (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, drinking), xlab='Year', group='frac2_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```


Age 60-69
=============================================================

Row
-------------------------------------------------------------


### 5 year risk of fracture (per 1000) (**Original**)

```{r}
tmp <- transform_orig(dat_annual_orig, 60, 70)
dygraph(tmp %>% select(yrs, risk_5yr), group='frac3')
```

### 5 year risk of fracture (per 1000) (**Offspring**)

```{r}
tmp2 <- transform_off(dat_annual_off, 60, 70)
dygraph(tmp2 %>% select(yrs, risk_5yr), group='frac3_off')
```

Row
---------------------------------------------------------------------

### Prevalence of obesity (**Original**)

```{r}
dygraph(tmp %>% select(yrs, obese), group = 'frac3') %>% 
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of obesity (**Offspring**)

```{r}

```


Row
---------------------------------------------------------------------------

### Prevalence of diabetes (**Original**)

```{r}
dygraph(tmp %>% select(yrs, diab),  group = 'frac3') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of diabetes (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, diab),  group = 'frac3_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

Row
-----------------------------------------------------------------

### Prevalence of smoking (**Original**)

```{r}
dygraph(tmp %>% select(yrs, smoking), group = 'frac3') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of smoking (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, smoking), group = 'frac3_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

Row
----------------------------------------------------------------------

### Prevalence of heavy drinking (**Original**)

```{r}
dygraph(tmp %>% select(yrs, drinking), xlab='Year', group='frac') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```


### Prevalence of heavy drinking (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, drinking), xlab='Year', group='frac_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```


Age 70-79
=============================================================

Row
-------------------------------------------------------------


### 5 year risk of fracture (per 1000) (**Original**)

```{r}
tmp <- transform_orig(dat_annual_orig, 70, 80)
dygraph(tmp %>% select(yrs, risk_5yr), group='frac4')
```

### 5 year risk of fracture (per 1000) (**Offspring**)

```{r}
tmp2 <- transform_off(dat_annual_off, 70, 80)
dygraph(tmp2 %>% select(yrs, risk_5yr), group='frac4_off')
```

Row
---------------------------------------------------------------------

### Prevalence of obesity (**Original**)

```{r}
dygraph(tmp %>% select(yrs, obese), group = 'frac4') %>% 
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of obesity (**Offspring**)

```{r}

```


Row
---------------------------------------------------------------------------

### Prevalence of diabetes (**Original**)

```{r}
dygraph(tmp %>% select(yrs, diab),  group = 'frac4') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of diabetes (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, diab),  group = 'frac4_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

Row
-----------------------------------------------------------------

### Prevalence of smoking (**Original**)

```{r}
dygraph(tmp %>% select(yrs, smoking), group = 'frac4') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of smoking (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, smoking), group = 'frac4_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

Row
----------------------------------------------------------------------

### Prevalence of heavy drinking (**Original**)

```{r}
dygraph(tmp %>% select(yrs, drinking), xlab='Year', group='frac4') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```


### Prevalence of heavy drinking (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, drinking), xlab='Year', group='frac4_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

Age 80+
=============================================================

Row
-------------------------------------------------------------


### 5 year risk of fracture (per 1000) (**Original**)

```{r}
tmp <- transform_orig(dat_annual_orig, 80, NA)
dygraph(tmp %>% select(yrs, risk_5yr), group='frac5')
```

### 5 year risk of fracture (per 1000) (**Offspring**)

```{r}
tmp2 <- transform_off(dat_annual_off, 80, NA)
dygraph(tmp2 %>% select(yrs, risk_5yr), group='frac5_off')
```

Row
---------------------------------------------------------------------

### Prevalence of obesity (**Original**)

```{r}
dygraph(tmp %>% select(yrs, obese), group = 'frac5') %>% 
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of obesity (**Offspring**)

```{r}

```


Row
---------------------------------------------------------------------------

### Prevalence of diabetes (**Original**)

```{r}
dygraph(tmp %>% select(yrs, diab),  group = 'frac5') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of diabetes (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, diab),  group = 'frac5_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

Row
-----------------------------------------------------------------

### Prevalence of smoking (**Original**)

```{r}
dygraph(tmp %>% select(yrs, smoking), group = 'frac5') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

### Prevalence of smoking (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, smoking), group = 'frac5_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```

Row
----------------------------------------------------------------------

### Prevalence of heavy drinking (**Original**)

```{r}
dygraph(tmp %>% select(yrs, drinking), xlab='Year', group='frac5') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```


### Prevalence of heavy drinking (**Offspring**)

```{r}
dygraph(tmp2 %>% select(yrs, drinking), xlab='Year', group='frac5_off') %>%
  dyAxis('y', axisLabelFormatter = 'function(d){return Math.round(d*100) + "%"}')
```
