---
title: "Notebook"
author: "Abhijit Dasgupta"
output:
  html_notebook: default
  html_document: default
---

## June 6, 2017

I evaluated the available data on Framingham. It seems that there are three corpuses of data. 

+ The original data from Framingham that doesn't contain any fracture data but contains all the other clinical information pertaining to the main cardiology study. This is stored in `archives`. 
+ A second corpus of data (stored in `newdat`), that contains fracture data from the exams. These files are given below:
```{r, warning=FALSE, echo=FALSE, message=FALSE}
ProjTemplate::reload()
datadir = set_datadir()
bl <- zipinfo(file.path(datadir,'newdat','framcohort.zip'))
bl$Name %>% str_subset('fx') %>% str_subset('Datasets')
bl <- zipinfo(file.path(datadir,'newdat/framoffspring.zip'))
bl$Name %>% str_subset('fx') %>% str_subset('Datasets')
```
+ A third corpus that contains a field for the computed year of fracture (computed as fxyear + Year of first exam) which isn't exactly correct, but nonetheless. 
```{r, echo=FALSE}
dir(path=file.path(datadir,'newdat.date'), pattern='sas7bdat', recursive=T)
```

The description of the various fields in each SAS dataset can be 
revealed since it is an attribute of the data set. For example, `sapply(d, attr, 'label')`. 

#### To do

1. Verification of fracture dates
2. Subdividing time into windows and verifying the incidence rates, both age-specific and age-standardized
3. Identification of files and fields containing risk factors, comorbidities, demographics

## June 7, 2017

I put `datadir` in `.Rprofile` so that it can automatically detect the operating system and adapt the path to the 
directory. I also put the data files on Dropbox, so that I can access it from anywhere. 

From my notes, the description of the central question of this study is as follows:

> What fraction of variability in the estimate of hip fracture incidence can be explained by risk factors and how does this change over time?

Table 1 in the paper would look at summaries of risk factors by decade (1970-2000).

# December 12, 2017

## Data Quality

Data is currently in an unusable pivot table format, that needs to be retrieved and rectified. This data is in 
the `munged` data folder


# January 9, 2018

The risk factors data sent by Tim was fixed and ingested using `tidyxl` means. Summaries were computed for all
the binary risk factors for three years: 1980, 1990, 2000. This is based on exam years 16, 21 and 26, from Tim's
analysis. 

Now we need to compute fracture incidence in those 3 years.

# Wed Feb 14 10:33:12 2018 ------------------------------

We are setting up the full Framingham data, both original and offspring cohorts, to allow time-varying
survival analysis and competing risks analysis. As of now, all but the smoking and drinking are done (these two require munging actual questionnaire data). 

The main analyses under consideration are:

1. A competing risks analysis with death as the competing risk. We can consider people censored if
they die over 2 years (my idea) after their last exam, else they are censored
2. A finer ecological analysis looking at prospective 5 year risks based on risk factors at each
year in the study.
