---
title: "Notebook"
author: "Abhijit Dasgupta"
output: html_notebook
---

## June 6, 2017

I evaluated the available data on Framingham. It seems that there are three corpuses of data. 

+ The original data from Framingham that doesn't contain any fracture data but contains all the other clinical information pertaining to the main cardiology study. This is stored in `archives`. 
+ A second corpus of data (stored in `newdat`), that contains fracture data from the exams. These files are given below:
```{r, warning=FALSE, echo=FALSE}
require(nat.utils)
require(stringr)
require(tidyverse)
datadir <- '/Users/abhijit/Dropbox/NIAMS/Bhattacharyya/Framingham/data'
bl <- zipinfo(file.path(datadir,'newdat','framcohort.zip'))
bl$Name %>% str_subset('fx') %>% str_subset('Datasets')
bl <- zipinfo(file.path(datadir,'newdat/framoffspring.zip'))
bl$Name %>% str_subset('fx') %>% str_subset('Datasets')
```
+ A third corpus that contains a field for the computed year of fracture (computed as fxyear + Year of first exam) which isn't exactly correct, but nonetheless. 
```{r, echo=FALSE}
dir(path=file.path(datadir,'newdat.date'), pattern='sas7bdat', recursive=T)
```

The description of the various fields in each SAS dataset can be 
revealed since it is an attribute of the data set. For example, `sapply(d, attr, 'label')`. 

#### To do

1. Verification of fracture dates
2. Subdividing time into windows and verifying the incidence rates, both age-specific and age-standardized
3. Identification of files and fields containing risk factors, comorbidities, demographics

## June 7, 2017

I put `datadir` in `.Rprofile` so that it can automatically detect the operating system and adapt the path to the 
directory. I also put the data files on Dropbox, so that I can access it from anywhere. 

